---
title: "Handling effect size dependency"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    df_print: paged
vignette: >
  %\VignetteIndexEntry{Handling effect size dependency}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
csl: https://zotero.org/styles/apa
bibliography: vignette.yaml
---

**Note: This vignette is a work in progress.** 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(psychmeta)
```

This vignette shows options for handling effect size dependency in **psychmeta**.
For more vignettes, see the [**psychmeta** overview](overview.html).

## Handling dependency
Psychometric meta-analysis assumes that each effect size for a particular construct relationship comes from an independent sample. If one sample provides multiple effect sizes for the same relationship, **psychmeta** can automatically consolidate them as either composites (recommended) or averages.

```{r, eval=FALSE}
ma_r(rxyi = rxyi, n = n, sample_id = sample_id,
     collapse_method = "composite",
     data = data_r_meas_multi)

ma_r(rxyi = rxyi, n = n, sample_id = sample_id,
     collapse_method = "average",
     data = data_r_meas_multi)
```
