---
title: "Heterogeneity analyses"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    df_print: paged
vignette: >
  %\VignetteIndexEntry{Heterogeneity analyses}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
csl: https://zotero.org/styles/apa
bibliography: vignette.yaml
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(psychmeta)
```

This vignette shows options for handling effect size dependency in **psychmeta**.
For more vignettes, see the [**psychmeta** overview](overview.html).


## Heterogeneity

## `heterogeneity()`

**`psychmeta`** automatically estimates residual standard deviations (_SD~res~_ and _SD~$\rho$~_) and credibility intervals. These statistics are the best way to examine heterogeneity in meta-anlayses [@WiernikEmpiricalBenchmarks2017]. The `heterogeneity()` function computes additional heterogeneity statistics (e.g., % Variance Accounted For, _Q_, _I_^2^) that may be requested by some journals or reviewers; we don't recommend these statistics for regular use.

```{r, eval=FALSE}
ma_obj <- heterogeneity(ma_obj)
```
