---
title: "Importing and organizing meta-analytic data"
output:
  rmarkdown::html_vignette:
    df_print: paged
bibliography: vignette.json
vignette: >
  %\VignetteIndexEntry{Importing and organizing meta-analytic data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
csl: https://zotero.org/styles/apa
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(psychmeta)
```

This vignette demonstrates workflows for importing and organizing meta-analytic
data for analysis with **psychmeta**. For more vignettes, see the **psychmeta**
[overview](overview.html).


## Data import

To import your data to R, we recommend the **rio** package. This `rio::import()`
function can conveniently import data sheets stored in most common formats. 
For an introduction to **rio**, see `vignette("rio", "rio")`.


## Data conversion and cleaning

**psychmeta** requires data to be in a "long" format. This means that each effect 
size is coded in its own row of a matrix. For example, a long format looks like this:

```{r, echo=FALSE}
# First 6 observations from the the database of Gonzalez-Mulé, Mount, and Oh (2014; JAP)
head(data_r_gonzalezmule_2014[,c("Study", "n", "rxyi", "Rating source",
                                "rxxi", "ryyi", "ux")])
```

Not all data come in a long format, so data manipulation tools can be helpful to convert it to a long format.

Recommended packages for data manipulation:

* **`dplyr`** (flexible package for fast, intuitive data manipulation)
* **`tidyr`** (functions to convert between wide and long data)

**`psychmeta`** can also help with reshaping data!

Sometimes it can be quick to code data in a journal table-like format:
```{r, include=FALSE}
dat_matrix <- data.frame(var_names = c("X", "Y", "Z"),
                         n = c(100, 100, 100),
                         mean = c(4, 5, 3),
                         sd = c(2.4, 2.6, 2),
                         rel = c(.8, .7, .85),
                         reshape_vec2mat(cov = c(.3, .4, .5),
                                         var_names = c("X", "Y", "Z")))
rownames(dat_matrix) <- NULL
```
```{r, eval=TRUE}
dat_matrix
```

This matrix-style format can be easily converted to the long-format data **`psychmeta`** requires with the `reshape_mat2dat()` function:

```{r, eval=TRUE}
reshape_mat2dat(
     var_names = var_names,                # Column of variable names
     cor_data = c("X", "Y", "X"),          # Names of correlation columns
     common_data = n,                      # Names of columns shared among relationships
     unique_data = c("mean", "sd", "rel"), # Names of columns unique to relationships
     data = dat_matrix)
```

\pagebreak

Sometimes it can also be quick to code data with multiple correlations in one row (i.e., a wide format):
```{r, include=FALSE}
dat_wide <- data.frame(sample_id = c(1, 2, 3),
                       ni = c(66, 74, 93),
                       rxyi_X_Y = c(-.29, -.16, -.34),
                       rxyi_X_Z = c(.18, .18, .02),
                       rxyi_Y_Z = c(.15, .00, .00),
                       rel_X   = c(.95, .93, .97),
                       rel_Y   = c(.85, .86, .82),
                       rel_Z   = c(.91, .90, .89))
```
```{r, eval=TRUE}
dat_wide
```

This wide format can be easily converted to the long format **`psychmeta`** requires:
```{r, eval=TRUE}
common_vars <- c("sample_id")           # Column names for variables common to all
                                        # relationships
var_names <- c("X", "Y", "Z")
es_design = matrix(NA, 3, 3)            # Matrix containing the column names
es_design[lower.tri(es_design)] <-      # for the intercorrelations among variables
  c("rxyi_X_Y", "rxyi_X_Z", "rxyi_Y_Z") # in the lower triangle of the matrix
rownames(es_design) <-
  colnames(es_design) <-
  var_names
n_design <- "ni"                        # Sample size column name or es_design-like
                                        # matrix
other_design <-                         # Matrix with variable names as row names,
  cbind(rel = c("rel_X",                # names of long-format variables as column names,
                 "rel_Y",               # and column names of dat_wide as elements
                 "rel_Z"))
rownames(other_design) <- var_names

reshape_wide2long(common_vars = common_vars,
                  es_design = es_design,
                  n_design = n_design,
                  other_design = other_design,
                  es_name = "rxyi",              # Type of effect size in dat_wide
                  data = dat_wide)
```

See also `vignette("pivot", "tidyr")`.
