---
title: "Meta-analyzing d values"
author: "Brenton Wiernik"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Meta-analyzing d values}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
csl: https://zotero.org/styles/apa
bibliography: vignette.yaml
---

**Note: This vignette is a work in progress.** 

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(psychmeta)
options(width = 160)
```

This vignette will walk you through estimating meta-analyses of
standardized mean differences (i.e., Cohen's _d_ or Hedges's _g_) between 
groups on multiple constructs.
For more vignettes, see the [**psychmeta** overview](overview.html).

## Getting Started

To begin, you will need your meta-analytic data sheet for analysis. We recommend
the **rio** package for importing data to **R**. For an introduction to **rio**, see
`vignette("rio", "rio")`.

**psychmeta** assumes that your data are in "long" format, with each row corresponding
to one effect size. For example, this is the format used in this data frame:

```{r}
coding_sheet <- 
  tibble::tribble(
    ~sample_id, ~construct,  ~n1,  ~n2,   ~d, ~ryyi,  ~rater,
            1L,        "X", 237L,  45L, 1.23,  0.83,  "self",
            1L,        "X", 237L,  45L, 0.95,  0.76, "other",
            1L,        "Y", 237L,  45L,  0.8,   0.7,  "self",
            1L,        "Y", 237L,  45L, 1.03,  0.64, "other",
            2L,        "X", 122L, 282L, 0.72,  0.76,  "self",
            2L,        "X", 122L, 282L, 1.14,  0.78, "other",
            2L,        "Y", 122L, 282L, 1.16,  0.78,  "self",
            2L,        "Y", 122L, 282L, 0.83,  0.76, "other",
            3L,        "X",  74L,  23L, 0.57,  0.76,  "self",
            3L,        "X",  74L,  23L, 0.75,  0.73, "other",
            3L,        "Y",  74L,  23L, 0.48,  0.68,  "self",
            3L,        "Y",  74L,  23L, 0.35,  0.73, "other",
            4L,        "X",  17L, 107L, 0.51,   0.7,  "self",
            4L,        "X",  17L, 107L, 0.78,  0.79, "other",
            4L,        "Y",  17L, 107L, 0.66,   0.7,  "self",
            4L,        "Y",  17L, 107L, 0.99,   0.8, "other",
            5L,        "X", 100L, 146L, 0.79,  0.73,  "self",
            5L,        "X", 100L, 146L, 1.03,  0.78, "other",
            5L,        "Y", 100L, 146L, 0.79,  0.72,  "self",
            5L,        "Y", 100L, 146L, 0.45,  0.69, "other"
    )

knitr::kable(coding_sheet)
```

In this table, 
  - **`sample_id`** contains labels indicating the sample each effect size is drawn from; 
  - **`construct`** indicates the variable/construct being compared in the effect size; 
  - **`n1`** and **`n2`** are the sample sizes for each group for the effect size; 
  - **`d`** is the Cohen's d effect size;
    - Values should be entered as Cohen's _d_, not Hedges's _g_ (i.e., not
      correcting for small-sample bias). Small-sample bias will be automatically
      corrected in the `ma_d()` function.
  - **`ryyi`** is the sample reliability values for the measures of the `construct` variables; 
  - **`rater`** here is a categorical moderator indicating whether the ratings were
    provided by the person themselves or another person.

You can see this data set includes group comparisons for two variables: `X` and `Y`, 
and that each sample contributes several effect sizes, one for each construct-rater
combination.

If your data are in a different format, you can use the `reshape_wide2long()`
function to reshape it. See the [import_organize](import_organize.html) vignette 
for details.

## Estimating a Barebones Meta-Analysis

Let's use the data frame above, called `coding_sheet`.

The primary function to conduct meta-analyses of _d_ values is `ma_d()`. To 
conduct barebones meta-analyses, run:

```{r}
ma_res <- ma_d(d = d, 
               n1 = n1,
               n2 = n2,
               construct_y = construct,
               sample_id = sample_id, 
               moderators = rater,
               data = coding_sheet
               )
```

- **`data`** is your data frame. 
- **`d`**, **`n1`**, **`n2`**, **`sample_id`**, and **`moderators`** are the 
  names of the columns in your data frame that contain the appropriate values. 
  - **`d`** is the Cohen's _d_ effect sizes; 
    - Values should be entered as Cohen's _d_, not Hedges's _g_ (i.e., not
      correcting for small-sample bias). Small-sample bias will be automatically
      corrected in the `ma_d()` function.
  - **`n1`** and **`n2`** are the group sample sizes; 
    - If `n2` is `NA`, then `n1` as the _total sample size_ across both groups.
  - **`construct_y`** are the labels for the variables/constructs being compared; 
  - **`sample_id`** is the sample identification labels; 
  - **`moderators`** is a vector of moderator variable names for the meta-analyses. 
  - Column names can be provided either with quotes (e.g., `"d"`, `"n1"`) or 
    without (e.g., `d`, `n1`).
- Multiple different group comparisons (e.g., Treatment 1 vs. Control;
  Treatment 2 vs. Control) by specifing the **`group_id`** or **`group1`**/**`group2`**
  columns:
    - **`group_id`** gives labels for the _comparison_ (e.g., "Treatment1-Control")
    - **`group1`** and **`group2`** give labels for the two groups in separate 
      columns (e.g., "Treatment1" in `group1` and "Control" in `group2`).

To conduct a barebones meta-analysis, at minimum, `n1` and `d` are needed.

### Modeling Options

- By default, Cohen's _d_ values are weighted by **effective sample size**.
  Effective sample size is computed as:
  
  $$N_{effective} = 4 \times \frac{n_{1} \times n_{2}}{n_{1} + n_{2}}$$
  
  This is similiar to weighting by total sample size, but account for increased
  uncertainty when group sizes are unequal [see @Bakbergenuly2019SMD].
  
  You can specify alternative weights using the `wt_type` argument.

- Random-effects variance (τ^2^ or *SD~res~*^2^) is estimated using the 
  Hunter-Schmidt estimator, computed using the unbiased sample variance estimator 
  (i.e., dividing by $k-1$ rather than $k$). To use the maximum-likelihood estimator
  instead, specify `var_unbiased = FALSE`.

- Barebones results are corrected for the small-sample bias in Cohen's _d_ 
  (i.e., results are Hedges's _g_ values). To disable this correction, 
  specify `correct_bias = FALSE`.

- By default, confidence and credibility intervals are constructed using a _t_
  distribution with $k-1$ degrees of freedom. To use a normal distribution instead,
  specify, `conf_method = "norm"` and `cred_method = "norm"`. To customize the
  coverage levels for these intervals, use the `conf_level` and `cred_level` arguments.

## The **psychmeta** Meta-Analysis Object

A **psychmeta** meta-analsyis object is a data frame, with each row being a meta-analysis 
or subanalysis and each column containing information about or results from that 
analysis. For example, the results of the analysis above look like this:

```{r}
ma_res
```

Each row corresponds to a different pair of variables/constructs (X-Y; X-Z; Y-Z)
and level of the moderator variable (overall/all levels pooled together; 
moderator = 1; moderator = 2).

- **`analysis_id`** is a numeric label for each analysis;
- **`pair_id`** is a numeric label for each combination of group comparison
  and variable/construct (Treatment1-Control differences on X; Treatment2-Control
  differences on Y); 
- **`group_contrast`** indicates the pair of groups being compared;
- **`construct_y`** indicates which variables/constructs are being compared.

- **`analysis_type`** indicates the type of analysis. 
  - "Overall" means an overall meta-analysis, pooling across all moderator levels. 
  - "Simple Moderator" means a subgroup moderator analysis of only studies with 
    the specified levels of the moderator variable(s) in the next column(s).

    (See below for how to conduct meta-analyses with multiple moderator variables
    or with continuous moderators)

- **`meta_tables`** contains the principal meta-analysis results tables.
- **`escalc`** contains tables of effect sizes, sampling error variances, weights, 
  residuals, and other data. These tables can be used for follow-up analyses or
  with the **metafor** package for additional meta-analysis techniques.

## Viewing Results Summaries

To view meta-anlaysis results tables, use the `summary()` function:

```{r}
summary(ma_res)
```

In this table, 

- **`analysis_id`**, **`pair_id`**, **`group_contrast`**, **`construct_y`**, and the
  moderator columns are defined as above.
- **`k`** is the number of effect sizes contributing to each meta-analysis. 
- **`N`** is the total sample size contributing to each meta-analysis.
- **`mean_d`** is the weighted mean Cohen's _d_ (Hedges's _g_) value.
- **`sd_d`** is the weighted observed standard deviation of _d_ (_g_) values.
- **`se_d`** is the standard error of `mean_d`. 
- **`sd_res`** is the estimated random-effects standard deviation (residual _SD_ 
  of _d_ [_g_] after accounting for sampling error). 
- **`CI_LL_95`** and **`CI_UL_95`** are the upper and lower bounds of the confidence 
  interval for `mean_d`; the number indicates the coverage level (default: 95%). 
- **`CR_LL_80`** and **`CR_UL_80`** are the upper and lower bounds of the credibility 
  interval for the estimated population distribution; the number indicates the 
  coverage level (default: 80%).

To view additional results, such as observed variance (`var_d`) or standard
deviation of sampling errors (`sd_e`), use the `get_metatab()` function and select
the appropriate columns:

```{r}
names(get_metatab(ma_res))

get_metatab(ma_res)$var_r
```

To view all columns of this table, convert it to a `data.frame` or `tibble`:

```{r}
dplyr::as_tibble(get_metatab(ma_res))
```

```{r}
as.data.frame(get_metatab(ma_res))
```

### Moderator Analyses

Results for subgroup analyses for different levels of categorical moderators are
shown in the rows of the meta-analysis results table. To estimate confidence
intervals for differences between levels or an omnibus ANOVA statistic, use the
`anova()` function:

```{r}
anova(ma_res)
```

### Correcting for Statistical Artifacts

See Artifact corrections](artifact_corrections.html).

## Outputting Results

To output the main meta-analysis results table to RMarkdown, Word, HTML, PDF, or 
other formats, use the `metabulate()` function. For example, to output the above 
results to a Word document, run:

```{r, eval=FALSE}
metabulate(ma_res, file = "meta-analysis_results.docx", output_format = "word")
```

## Follow-Up Analyses

### Plotting

You can add plots for each meta-analysis in `ma_res` using the `plot_forest()`
and `plot_funnel()` functions:

```{r}
ma_res <- plot_funnel(ma_res)
ma_res <- plot_forest(ma_res)
```

You can view these plots using the `get_plots()` function. This will return a
list of all of the plots in this results. Specify which meta-analysis you want 
to view plots for by passing its `analysis_id` to `[[`:

```{r, fig.show='hold'}
get_plots(ma_res)[["forest"]][[2]]
get_plots(ma_res)[["funnel"]][[2]]
```

For forest plots, if you select an "Overall" meta-analysis, it will include 
plots faceted by moderator levels (`"moderated"`) and not (`"unmoderated"`):

```{r, fig.show='hold'}
get_plots(ma_res)[["forest"]][[1]][["moderated"]][["barebones"]]
get_plots(ma_res)[["forest"]][[1]][["unmoderated"]][["barebones"]]
```

### Heterogeneity Analyses

**psychmeta** reports the random-effects standard deviaton (τ or *SD_res_*) 
and credibility intervals (`mean_r` ± _crit_ × *SD~res~*) in the main 
meta-analaysis results tables. To view confidence intervals for *SD_res_* or 
additional heterogeneity statistics, use the `heterogeneity()` function:

```{r}
ma_res <- heterogeneity(ma_res)
get_heterogeneity(ma_res)[[1]][["barebones"]]
```

### Publication Bias and Sensitivity Analyses

**psychmeta** supports cumulative meta-analysis for publication/small-sample bias
detection, leave-1-out sensitivity analyses, and bootstrap confidence intervals
using the sensitivity function:

```{r, fig.show='hold'}
ma_res <- sensitivity(ma_res)
get_cumulative(ma_res)[[1]][["barebones"]]
get_cumulative(ma_res)[[1]][["barebones"]][["plots"]]
```

```{r}
get_bootstrap(ma_res)[[1]][["barebones"]]
```

# Bibliography
