---
title: "Welcome to **psychmeta**!"
output:
  rmarkdown::html_vignette:
    df_print: paged
bibliography: vignette.json
vignette: >
  %\VignetteIndexEntry{* psychmeta overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
csl: https://zotero.org/styles/apa
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(psychmeta)
```

**psychmeta** is a comprehensive package for computing psychometric meta-analyses, 
organizing meta-analytic data, conducting follow-up analyses of meta-analytic 
results (e.g., cumulative meta-analyses, leave-one-out meta-analyses, bootstrapped 
meta-analyses, and meta-regressions), simulating data impacted by psychometric 
artifacts, and much more! 

This tutorial is meant to introduce you to some of the most critical features of 
**psychmeta** and familiarize you with workflows within the package.

# Installing and loading **psychmeta**

Install the official CRAN version of the package:
```{r, eval=FALSE}
install.packages("psychmeta")
```

Or install the GitHub verson (with incremental updates between CRAN releases):
```{r, eval=FALSE}
devtools::install_github("psychmeta/psychmeta")
```

Load the package library:
```{r, eval=FALSE}
library(psychmeta)
```

## **psychmeta** vignettes

The following vignettes show workflows for common tasks in **psychmeta**:

  - [Import and organize meta-analytic data](import_organize.html)
  - [Effect size conversion and sporadic artifact correction](es_conversion.html)
  - Computing meta-analyses
    - [Barebones meta-analysis: Correlations](barebones_r.html)
    - [Barebones meta-analysis: d values](barebones_d.html)
    - [Individual-corrections meta-analysis: Correlations](ic_r.html)
    - [Individual-corrections meta-analysis: d values](ic_d.html)
    - [Artifact-distribution meta-analysis: Correlations](ad_r.html)
    - [Artifact-distribution meta-analysis: d values](ad_d.html)
    - [Generic effect size meta-analysis](ma_generic.html)
  - Follow-up analyses
    - [Sensitivity analyses](sensitivity.html)
      - Publication bias, leave-one-out, bootstrap confidence intervals
    - [Moderator analyses](moderator_analysis.html)
    - [Outpur results in Word, PDF, HTML, or Markdown](output_results.html)
      - Results tables, bibliographies of included studies
    - [Plots](plots.html)
    
Additional topics: 

  - [Meta-analysis arguments and options](ma_options.html)
  - [Simulating psychometric data and meta-analyses](simulation.html)
  - [Composite effect sizes and psychometric artifacts](composites.html)
  - [Effect size dependency](dependency.html)
  - [Matrix regression](matrix_regression.html)
  - [Multivariate range-restriction correction](multivariate_range_restriction.html)


## Best practices for publishing with **`psychmeta`**:

1. Include your R script in an online supplement.
2. Include your data table as a CSV in an online supplement.
3. Cite **psychmeta**.
     - Please reference our software announcement in 
       *Applied Psychological Measurement* [@Dahlkepsychmetapackagepsychometric2019].

# Bibliography
