---
title: "Sensitivity Analyses"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    df_print: paged
vignette: >
  %\VignetteIndexEntry{Sensitivity analyses}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(psychmeta)
```

## Heterogeneity

## `sensitivity()`

`sensitivity()` computes several different types of sensitivity analyses for meta-analytic results:

* `bootstrap` (calculate bootstrap confidence intervals on all meta-analysis results)
* `cumulative` (calculate cumulative meta-analyses—a form of publication bias analysis)
* `leave1out` (compute meta-anlayses leaving out 1 sample at a time—for outlier/influential point detection)

You can either call all sensitivity analyses at once (`sensitivity()`) or call each type of analysis individually (`sensitivity_bootstrap()`, `sensitivity_cumulative()`, `sensitivity_leave1out()`):
```{r, eval=FALSE}
ma_obj <- sensitivity(ma_obj,
                      leave1out = TRUE,
                      bootstrap = TRUE,
                      cumulative = TRUE,

                      sort_method = "weight",

                      boot_iter = 100,
                      boot_conf_level = 0.95,
                      boot_ci_type = "norm")
```
